A Dynamic Intrafamily Model of Child Behavior Problems and Birth Timing

### 2018-04-11 inst/paper/diagram.tex
Updates literally everywhere

\documentclass{standalone}
\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}
\begin{document}

<<setup, include=FALSE>>=
load("./naive_tidy.RData")

naive_tidy$est <- round(naive_tidy$est,2)
naive_tidy$se <- round(naive_tidy$se,2)

b_m_age_1_diff_1 <- naive_tidy$est[3]; se_b_m_age_1_diff_1 <- naive_tidy$se[3]
b_m_age_2_diff_2 <- naive_tidy$est[4]; se_b_m_age_2_diff_2 <- naive_tidy$se[4]
cov_m_age_1_fe   <- naive_tidy$est[5]; se_cov_m_age_1_fe   <- naive_tidy$se[5]
cov_m_age_2_fe   <- naive_tidy$est[6]; se_cov_m_age_2_fe   <- naive_tidy$se[6]
cov_m_age <- naive_tidy$est[7]; se_cov_m_age   <- naive_tidy$se[7]
b_inst      <- naive_tidy$est[8];  se_inst     <- naive_tidy$se[8]
diff_1_err  <- naive_tidy$est[9];  diff_2_err  <- naive_tidy$est[10]
m_age_1_err <- naive_tidy$est[11]; m_age_2_err <- naive_tidy$est[12]
fe_err      <- naive_tidy$est[13]
# setwd("./paper")
@

@@

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
     \node [cloud] (F) {$Shared\ Component_{i}$ (FE)};
     \node [block, above left= 1cm and -1.5cm of F] (T1) {$Mother Age_{1i}$ (T1)};
     \node [block, below left= 1cm and -1.5cm of F] (T2) {$Mother Age_{2i}$ (T2)};
     \node [block, right of=T1, node distance=6cm] (BP1) {$Difficulty_{1i}$ (BP1)};
     \node [block, right of=T2, node distance=6cm] (BP2) {$Difficulty_{2i}$ (BP2)};
     \node [right of=BP1, node distance=3cm] (E1) {\Sexpr{diff_1_err}};
     \node [right of=BP2, node distance=3cm] (E2) {\Sexpr{diff_2_err}};
     \node [left of=T1, node distance=2cm] (pt1) {\Sexpr{m_age_1_err}};
     \node [left of=T2, node distance=2cm] (pt2) {\Sexpr{m_age_2_err}};
     \node [below of=pt1, node distance=1.85cm] (pf) {\Sexpr{fe_err}};
     \node [below right= 2.5cm and 5.3cm of F] (ee) {$ $};
     \node [below right= 2.5cm and -2.5cm of F] (eek) {$ $};
     \node [below = .72cm of E2] (eej) {$ $};
     \node [below right= 0cm and 5.8cm of F, align=center] (ee2) {\Sexpr{b_inst}\\ (\Sexpr{se_inst})};
     \node [left of=F, node distance=5.4cm, align=center] (stt) {\Sexpr{cov_m_age}\\ (\Sexpr{se_cov_m_age})};
     \node [above left= .2cm and 1.4cm of F, align=center] (st1f) {\Sexpr{cov_m_age_1_fe}\\ (\Sexpr{se_cov_m_age_1_fe})};
     \node [below left= .2cm and 1.4cm of F, align=center] (st2f) {\Sexpr{cov_m_age_2_fe}\\ (\Sexpr{se_cov_m_age_2_fe})};
     \node [above right= .7cm and -.1cm of F] (sfbp1) {$1$};
     \node [below right= .2cm and -.1cm of F] (sfbp2) {$1$};
     \node [above right= 1.5cm and -1.9cm of F, align=center] (stbp1) {\Sexpr{b_m_age_1_diff_1}\\ (\Sexpr{se_b_m_age_1_diff_1})};
     \node [below right= .6cm and -1.9cm of F, align=center] (stbp1) {\Sexpr{b_m_age_2_diff_2}\\ (\Sexpr{se_b_m_age_2_diff_2})};
    % Draw edges
    \draw [->] (T1) to (BP1);
    \draw [->] (T2) to (BP2);
    \draw [->] (F) to (BP1);
    \draw [->] (F) to (BP2);
    \draw [->] (E1) to (BP1);
    \draw [->] (E2) to (BP2);
    \draw [->] (pt1) to (T1);
    \draw [->] (pt2) to (T2);
    \draw [->] (pf) to (F);
    \path (pt1) edge [<->, bend right=90, looseness=1.5] node {$ $} (pt2);
    \path (pt1) edge [<->, out=180,in=180] node {$ $} (pf);
    \path (pt2) edge [<->, out=180,in=180] node {$ $} (pf);
    \draw [-] (E1) to [out=0,in=90] (ee2);
    \draw [->] (ee2) to [out=270,in=0] (eej)
    to [out=180, in=0] (eek)
    to [out=180,in=270, looseness=1] (T2);
\end{tikzpicture}

>>>>

\documentclass{standalone}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
     \node [cloud] (F) {$Shared\ Component_{i}$ (FE)};
     \node [block, above left= 1cm and -1.5cm of F] (T1) {$Mother Age_{1i}$ (T1)};
     \node [block, below left= 1cm and -1.5cm of F] (T2) {$Mother Age_{2i}$ (T2)};
     \node [block, right of=T1, node distance=6cm] (BP1) {$Difficulty_{1i}$ (BP1)};
     \node [block, right of=T2, node distance=6cm] (BP2) {$Difficulty_{2i}$ (BP2)};
     \node [right of=BP1, node distance=3cm] (E1) {35.5};
     \node [right of=BP2, node distance=3cm] (E2) {46.93};
     \node [left of=T1, node distance=2cm] (pt1) {13.8};
     \node [left of=T2, node distance=2cm] (pt2) {15.83};
     \node [below of=pt1, node distance=1.85cm] (pf) {23.23};
     \node [below right= 2.5cm and 5.3cm of F] (ee) {$ $};
     \node [below right= 2.5cm and -2.5cm of F] (eek) {$ $};
     \node [below = .72cm of E2] (eej) {$ $};
     \node [below right= 0cm and 5.8cm of F, align=center] (ee2) {-5.98\\ (2.68)};
     \node [left of=F, node distance=5.4cm, align=center] (stt) {11.94\\ (0.5)};
     \node [above left= .2cm and 1.4cm of F, align=center] (st1f) {13.91\\ (6.23)};
     \node [below left= .2cm and 1.4cm of F, align=center] (st2f) {18.26\\ (8.08)};
     \node [above right= .7cm and -.1cm of F] (sfbp1) {$1$};
     \node [below right= .2cm and -.1cm of F] (sfbp2) {$1$};
     \node [above right= 1.5cm and -1.9cm of F, align=center] (stbp1) {-1.74\\ (0.48)};
     \node [below right= .6cm and -1.9cm of F, align=center] (stbp1) {-1.74\\ (0.48)};
    % Draw edges
    \draw [->] (T1) to (BP1);
    \draw [->] (T2) to (BP2);
    \draw [->] (F) to (BP1);
    \draw [->] (F) to (BP2);
    \draw [->] (E1) to (BP1);
    \draw [->] (E2) to (BP2);
    \draw [->] (pt1) to (T1);
    \draw [->] (pt2) to (T2);
    \draw [->] (pf) to (F);
    \path (pt1) edge [<->, bend right=90, looseness=1.5] node {$ $} (pt2);
    \path (pt1) edge [<->, out=180,in=180] node {$ $} (pf);
    \path (pt2) edge [<->, out=180,in=180] node {$ $} (pf);
    \draw [-] (E1) to [out=0,in=90] (ee2);
    \draw [->] (ee2) to [out=270,in=0] (eej)
    to [out=180, in=0] (eek)
    to [out=180,in=270, looseness=1] (T2);
\end{tikzpicture}

### 2018-04-11 inst/paper/diagram_estimates.Rnw
Updates literally everywhere

<<setup, include=FALSE>>=
load("./naive_tidy.RData")

@@

b_m_age_1_diff_1 <- naive_tidy$est[3]; se_b_m_age_1_diff_1 <- naive_tidy$se[3]
b_m_age_2_diff_2 <- naive_tidy$est[4]; se_b_m_age_2_diff_2 <- naive_tidy$se[4]
cov_m_age_1_fe   <- naive_tidy$est[5]; se_cov_m_age_1_fe   <- naive_tidy$se[5]
cov_m_age_2_fe   <- naive_tidy$est[6]; se_cov_m_age_2_fe   <- naive_tidy$se[6]
cov_m_age <- naive_tidy$est[7]; se_cov_m_age   <- naive_tidy$se[7]
b_inst      <- naive_tidy$est[8];  se_inst     <- naive_tidy$se[8]
diff_1_err  <- naive_tidy$est[9];  diff_2_err  <- naive_tidy$est[10]
m_age_1_err <- naive_tidy$est[11]; m_age_2_err <- naive_tidy$est[12]
fe_err      <- naive_tidy$est[13]
# setwd("./paper")
@

>>>>

<<setup, include=FALSE>>=
load("../data/derived_data/naive_tidy.RData")

# For ease, I have just extracted all relevant values and assigned them.

@@

b_m_age_1_diff_1 <- naive_tidy$est[3]; se_b_m_age_1_diff_1 <- naive_tidy$se[3]
b_m_age_2_diff_2 <- naive_tidy$est[4]; se_b_m_age_2_diff_2 <- naive_tidy$se[4]
cov_m_age_1_fe   <- naive_tidy$est[5]; se_cov_m_age_1_fe   <- naive_tidy$se[5]
cov_m_age_2_fe   <- naive_tidy$est[6]; se_cov_m_age_2_fe   <- naive_tidy$se[6]
cov_m_age <- naive_tidy$est[7]; se_cov_m_age   <- naive_tidy$se[7]
b_inst      <- naive_tidy$est[8];  se_inst     <- naive_tidy$se[8]
diff_1_err  <- naive_tidy$est[9];  diff_2_err  <- naive_tidy$est[10]
m_age_1_err <- naive_tidy$est[11]; m_age_2_err <- naive_tidy$est[12]
fe_err      <- naive_tidy$est[13]

@

### 2018-04-11 inst/paper/diagram_model.Rnw
Updates literally everywhere

<<setup, include=FALSE>>=
load("../data/derived_data/naive_tidy.RData")

# For ease, I have just extracted all relevant values and assigned them.

naive_tidy$est <- round(naive_tidy$est,2)
naive_tidy$se <- round(naive_tidy$se,2)

b_m_age_1_diff_1 <- naive_tidy$est[3]; se_b_m_age_1_diff_1 <- naive_tidy$se[3]
b_m_age_2_diff_2 <- naive_tidy$est[4]; se_b_m_age_2_diff_2 <- naive_tidy$se[4]
cov_m_age_1_fe   <- naive_tidy$est[5]; se_cov_m_age_1_fe   <- naive_tidy$se[5]
cov_m_age_2_fe   <- naive_tidy$est[6]; se_cov_m_age_2_fe   <- naive_tidy$se[6]
cov_m_age <- naive_tidy$est[7]; se_cov_m_age   <- naive_tidy$se[7]
b_inst      <- naive_tidy$est[8];  se_inst     <- naive_tidy$se[8]
diff_1_err  <- naive_tidy$est[9];  diff_2_err  <- naive_tidy$est[10]
m_age_1_err <- naive_tidy$est[11]; m_age_2_err <- naive_tidy$est[12]
fe_err      <- naive_tidy$est[13]

@

@@

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
     \node [cloud] (F) {$Shared\ Component_{i}$ (FE)};
     \node [block, above left= 1cm and -1.5cm of F] (T1) {$Mother Age_{1i}$ (T1)};
     \node [block, below left= 1cm and -1.5cm of F] (T2) {$Mother Age_{2i}$ (T2)};
     \node [block, right of=T1, node distance=6cm] (BP1) {$Difficulty_{1i}$ (BP1)};
     \node [block, right of=T2, node distance=6cm] (BP2) {$Difficulty_{2i}$ (BP2)};
     \node [right of=BP1, node distance=3cm] (E1) {\Sexpr{diff_1_err}};
     \node [right of=BP2, node distance=3cm] (E2) {\Sexpr{diff_2_err}};
     \node [left of=T1, node distance=2cm] (pt1) {\Sexpr{m_age_1_err}};
     \node [left of=T2, node distance=2cm] (pt2) {\Sexpr{m_age_2_err}};
     \node [below of=pt1, node distance=1.85cm] (pf) {\Sexpr{fe_err}};
     \node [below right= 2.5cm and 5.3cm of F] (ee) {$ $};
     \node [below right= 2.5cm and -2.5cm of F] (eek) {$ $};
     \node [below = .72cm of E2] (eej) {$ $};
     \node [below right= 0cm and 5.8cm of F, align=center] (ee2) {\Sexpr{b_inst}\\ (\Sexpr{se_inst})};
     \node [left of=F, node distance=5.4cm, align=center] (stt) {\Sexpr{cov_m_age}\\ (\Sexpr{se_cov_m_age})};
     \node [above left= .2cm and 1.4cm of F, align=center] (st1f) {\Sexpr{cov_m_age_1_fe}\\ (\Sexpr{se_cov_m_age_1_fe})};
     \node [below left= .2cm and 1.4cm of F, align=center] (st2f) {\Sexpr{cov_m_age_2_fe}\\ (\Sexpr{se_cov_m_age_2_fe})};
     \node [above right= .7cm and -.1cm of F] (sfbp1) {$1$};
     \node [below right= .2cm and -.1cm of F] (sfbp2) {$1$};
     \node [above right= 1.5cm and -1.9cm of F, align=center] (stbp1) {\Sexpr{b_m_age_1_diff_1}\\ (\Sexpr{se_b_m_age_1_diff_1})};
     \node [below right= .6cm and -1.9cm of F, align=center] (stbp1) {\Sexpr{b_m_age_2_diff_2}\\ (\Sexpr{se_b_m_age_2_diff_2})};
    % Draw edges
    \draw [->] (T1) to (BP1);
    \draw [->] (T2) to (BP2);
    \draw [->] (F) to (BP1);
    \draw [->] (F) to (BP2);
    \draw [->] (E1) to (BP1);
    \draw [->] (E2) to (BP2);
    \draw [->] (pt1) to (T1);
    \draw [->] (pt2) to (T2);
    \draw [->] (pf) to (F);
    \path (pt1) edge [<->, bend right=90, looseness=1.5] node {$ $} (pt2);
    \path (pt1) edge [<->, out=180,in=180] node {$ $} (pf);
    \path (pt2) edge [<->, out=180,in=180] node {$ $} (pf);
    \draw [-] (E1) to [out=0,in=90] (ee2);
    \draw [->] (ee2) to [out=270,in=0] (eej)
    to [out=180, in=0] (eek)
    to [out=180,in=270, looseness=1] (T2);
\end{tikzpicture}

>>>>

@@

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
     \node [cloud] (F) {$Shared\ Component_{i}$ (FE)};
     \node [block, above left= 1cm and -1.5cm of F] (T1) {$Mother Age_{1i}$ (T1)};
     \node [block, below left= 1cm and -1.5cm of F] (T2) {$Mother Age_{2i}$ (T2)};
     \node [block, right of=T1, node distance=6cm] (BP1) {$Difficulty_{1i}$ (BP1)};
     \node [block, right of=T2, node distance=6cm] (BP2) {$Difficulty_{2i}$ (BP2)};
     \node [right of=BP1, node distance=3cm] (E1) {$\epsilon_{1i}$};
     \node [right of=BP2, node distance=3cm] (E2) {$\epsilon_{2i}$};
     \node [below right= 2.5cm and 5.3cm of F] (ee) {$ $};
     \node [below right= 2.5cm and -2.5cm of F] (eek) {$ $};
     \node [below right= 0cm and 5.8cm of F] (ee2) {$\sigma_{\epsilon_{1i}T_{2i}}$};
     \node [left of=F, node distance=3.9cm] (stt) {$\sigma_{T_{1i}T_{2i}}$};
     \node [above left= .33cm and .1cm of F] (st1f) {$\sigma_{T_{1i}FE_{i}}$};
     \node [below left= .33cm and .1cm of F] (st2f) {$\sigma_{T_{2i}FE_{i}}$};
     \node [above right= .29cm and .4cm of F] (sfbp1) {$\gamma_{FE_{i}BP_{1i}} = 1$};
     \node [below right= .3cm and .4cm of F] (sfbp2) {$\gamma_{FE_{i}BP_{2i}} = 1$};
     \node [above right= 1.5cm and -1.4cm of F] (stbp1) {$\gamma_{T_{1i}BP_{1i}}$};
     \node [below right= 1.55cm and -1.4cm of F] (stbp2) {$\gamma_{T_{2i}BP_{2i}}$};
    % Draw edges
    \path [line] (T1) -- (BP1);
    \path [line] (T2) -- (BP2);
    \path [line] (F) -- (BP1);
    \path [line] (F) -- (BP2);
    \path [line] (E1) -- (BP1);
    \path [line] (E2) -- (BP2);
    \path (T1) edge [<->, bend right=90, looseness=1.5] node {$ $} (T2);
    \path (T1) edge [<->, out=180,in=180] node {$ $} (F);
    \path (T2) edge [<->, out=180,in=180] node {$ $} (F);
    \draw [->] (E1) to [out=0,in=0] (ee)
    to [out=180,in=0, looseness=.35] (eek)
    to [out=180,in=270, looseness=1] (T2);
\end{tikzpicture}

### 2018-04-11 inst/paper/diagram_model.tex
Updates literally everywhere

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
     \node [cloud] (F) {$Shared\ Component_{i}$ (FE)};
     \node [block, above left= 1cm and -1.5cm of F] (T1) {$Mother Age_{1i}$ (T1)};
     \node [block, below left= 1cm and -1.5cm of F] (T2) {$Mother Age_{2i}$ (T2)};
     \node [block, right of=T1, node distance=6cm] (BP1) {$Difficulty_{1i}$ (BP1)};
     \node [block, right of=T2, node distance=6cm] (BP2) {$Difficulty_{2i}$ (BP2)};
     \node [right of=BP1, node distance=3cm] (E1) {35.5};
     \node [right of=BP2, node distance=3cm] (E2) {46.93};
     \node [left of=T1, node distance=2cm] (pt1) {13.8};
     \node [left of=T2, node distance=2cm] (pt2) {15.83};
     \node [below of=pt1, node distance=1.85cm] (pf) {23.23};
     \node [below right= 2.5cm and 5.3cm of F] (ee) {$ $};
     \node [below right= 2.5cm and -2.5cm of F] (eek) {$ $};
     \node [below = .72cm of E2] (eej) {$ $};
     \node [below right= 0cm and 5.8cm of F, align=center] (ee2) {-5.98\\ (2.68)};
     \node [left of=F, node distance=5.4cm, align=center] (stt) {11.94\\ (0.5)};
     \node [above left= .2cm and 1.4cm of F, align=center] (st1f) {13.91\\ (6.23)};
     \node [below left= .2cm and 1.4cm of F, align=center] (st2f) {18.26\\ (8.08)};
     \node [above right= .7cm and -.1cm of F] (sfbp1) {$1$};
     \node [below right= .2cm and -.1cm of F] (sfbp2) {$1$};
     \node [above right= 1.5cm and -1.9cm of F, align=center] (stbp1) {-1.74\\ (0.48)};
     \node [below right= .6cm and -1.9cm of F, align=center] (stbp1) {-1.74\\ (0.48)};
    % Draw edges
    \draw [->] (T1) to (BP1);
    \draw [->] (T2) to (BP2);
    \draw [->] (F) to (BP1);
    \draw [->] (F) to (BP2);
    \draw [->] (E1) to (BP1);
    \draw [->] (E2) to (BP2);
    \draw [->] (pt1) to (T1);
    \draw [->] (pt2) to (T2);
    \draw [->] (pf) to (F);
    \path (pt1) edge [<->, bend right=90, looseness=1.5] node {$ $} (pt2);
    \path (pt1) edge [<->, out=180,in=180] node {$ $} (pf);
    \path (pt2) edge [<->, out=180,in=180] node {$ $} (pf);
    \draw [-] (E1) to [out=0,in=90] (ee2);
    \draw [->] (ee2) to [out=270,in=0] (eej)
    to [out=180, in=0] (eek)
    to [out=180,in=270, looseness=1] (T2);
\end{tikzpicture}

>>>>

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
     \node [cloud] (F) {$Shared\ Component_{i}$ (FE)};
     \node [block, above left= 1cm and -1.5cm of F] (T1) {$Mother Age_{1i}$ (T1)};
     \node [block, below left= 1cm and -1.5cm of F] (T2) {$Mother Age_{2i}$ (T2)};
     \node [block, right of=T1, node distance=6cm] (BP1) {$Difficulty_{1i}$ (BP1)};
     \node [block, right of=T2, node distance=6cm] (BP2) {$Difficulty_{2i}$ (BP2)};
     \node [right of=BP1, node distance=3cm] (E1) {$\epsilon_{1i}$};
     \node [right of=BP2, node distance=3cm] (E2) {$\epsilon_{2i}$};
     \node [below right= 2.5cm and 5.3cm of F] (ee) {$ $};
     \node [below right= 2.5cm and -2.5cm of F] (eek) {$ $};
     \node [below right= 0cm and 5.8cm of F] (ee2) {$\sigma_{\epsilon_{1i}T_{2i}}$};
     \node [left of=F, node distance=3.9cm] (stt) {$\sigma_{T_{1i}T_{2i}}$};
     \node [above left= .33cm and .1cm of F] (st1f) {$\sigma_{T_{1i}FE_{i}}$};
     \node [below left= .33cm and .1cm of F] (st2f) {$\sigma_{T_{2i}FE_{i}}$};
     \node [above right= .29cm and .4cm of F] (sfbp1) {$\gamma_{FE_{i}BP_{1i}} = 1$};
     \node [below right= .3cm and .4cm of F] (sfbp2) {$\gamma_{FE_{i}BP_{2i}} = 1$};
     \node [above right= 1.5cm and -1.4cm of F] (stbp1) {$\gamma_{T_{1i}BP_{1i}}$};
     \node [below right= 1.55cm and -1.4cm of F] (stbp2) {$\gamma_{T_{2i}BP_{2i}}$};
    % Draw edges
    \path [line] (T1) -- (BP1);
    \path [line] (T2) -- (BP2);
    \path [line] (F) -- (BP1);
    \path [line] (F) -- (BP2);
    \path [line] (E1) -- (BP1);
    \path [line] (E2) -- (BP2);
    \path (T1) edge [<->, bend right=90, looseness=1.5] node {$ $} (T2);
    \path (T1) edge [<->, out=180,in=180] node {$ $} (F);
    \path (T2) edge [<->, out=180,in=180] node {$ $} (F);
    \draw [->] (E1) to [out=0,in=0] (ee)
    to [out=180,in=0, looseness=.35] (eek)
    to [out=180,in=270, looseness=1] (T2);
\end{tikzpicture}
